A Reproducible Data Analysis Workflow with RMarkdown, Git, Make & Docker

### 2019-10-29 rr-flow.Rmd
solves #54

For other distributions, replace `apt` with the native package manager. One may need elevated rights for the installation; in this case add `sudo` before the installation command. `docker` also needs elevated rights to run; therefore, we recomend to add the local user to the `docker` group, following the [documentation of docker](https://docs.docker.com/install/linux/linux-postinstall/#manage-docker-as-a-non-root-user).

@@

In our own experience, it is often not possible to convince all co-authors to switch to a different document processing environment, such as RMarkdown. That is, we have experienced that after writing up the first draft in Rmarkdown, one must eventually to genereate a Word-file that is from then on used as static file serving as a basis for multiple iterations among the co-authors. Reteining reproduciblity in such situation requires tediues manuel synchronization. This labor can be saved with the [rodoc package](https://noamross.github.io/redoc/articles/mixed-workflows-with-redoc.html) [@redoc], which enables a two-way workflow between Word and Rmarkdown. The conversion between Rmarkdown and Word retains all changes and even supports words tracked changes feature.

>>>>

For other distributions, replace `apt` with the native package manager. You may need elevated rights for the installation; in this case add `sudo` before the installation command. `docker` also needs elevated rights to run; therefore, we recomend to add the local user to the `docker` group, following the [documentation of docker](https://docs.docker.com/install/linux/linux-postinstall/#manage-docker-as-a-non-root-user).

@@

In our own experience, it is often not possible to convince all co-authors to switch to a different document processing environment, such as RMarkdown. That is, we have experienced that after writing up the first draft in Rmarkdown, one must eventually genereate a Word-file that is from then on used as static file serving as a basis for multiple iterations among the co-authors. Reteining reproduciblity in such situation requires tediues manuel synchronization. This labor can be saved with the [rodoc package](https://noamross.github.io/redoc/articles/mixed-workflows-with-redoc.html) [@redoc], which enables a two-way workflow between Word and Rmarkdown. The conversion between Rmarkdown and Word retains all changes and even supports words tracked changes feature.
